IN5490 Project

### 2023-10-02 doc/paper.tex
update paper
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>

@@

One of the central challenges of reinforcement learning is that rewards are often both extremely rare and delayed, which means that optimizing a reinforcement learning algorithm requires significant trial and error \cite[423]{brunton}.

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

@@

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

@@

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

>>>>

Reinforcement Learning!

@@

One of the central challenges of reinforcement learning is that rewards are often both extremely rare and delayed, which means that optimizing a reinforcement learning algorithm requires significant trial and error \cite[423]{brunton}. Furthermore, in many problems the state-action spaces are enormous, meaning that uniform exploration is unlikely to find good solutions in a reasonable amount of time. Many methods have been developed to deal with this issue, for example by introducing auxilliary reward functions that use domain knowledge, or which reward the agent for learning novel skills. However, hand picking which actions to reward can lead to imitation rather than optimal behaviour, and novelty is not always useful \cite[2]{ellm}. With the introduction of Large Language Models (LLMs), a new area of research has opened up, attempting to use the vast amount of human knowledge encoded in these models to increase the performance of reinforcement learning algorithms \cite{survey}. These

\section{Background and Related Work}

 Degus is the future in blockchain techonology, created by using the revolutionary "degus system", which creates twice as many coins per unit of computational power. By accepting the "degus mindset", you will be able to acheive things you never ever thought possible. The degus mindset includes the following:

Always Striving for Excellence
Generate passive revenue through the degus system
Live day by day: "Carpe diem"

By following these simple steps, and by buying several GPUs, you will be able to produce around 15 deguscoins per computational unit, unleashing the true power of the blockchain.

What is the deguscoin, you may ask? The deguscoin represents a complete transformation of the traditional financial system (tradfi). By using deguscoin, you will be able to achieve returns of investment (ROIs) beyond mere human comprehension. One single deguscoin, when inserted into an economy, can have such destructive power that even mere days after, the market will be beyond recognition. By invoking the "degus mindset" (DM) you will be able to send around 15\% more currency per coin, achieving ROIs which would send the average economist into a seizure.

Market players are predicting that by the end of this year, around 50\% of all transactions will be done under the degus system (DS), not even counting derivatives.

By the end of this year, around 50\% of all transactions will be done under the degus system, not even counting derivatives.

– Market players

What are you waiting for? Purchase deguscoin right now, and leave your earthly desires behind!

\section{Method}

Deguser trenger god plass for å trives, og du bør investere i et størst mulig bur som gir dyrene mulighet til å klatre, grave i et tykt strølag og bevege seg i flere etasjer.

Mange dyreeiere konstruerer sine egne løsninger, for eksempel med et stort, gammelt akvarium som underdel og et nettingbur på toppen av dette. Da får du full oversikt over hva som skjer også nederst i buret, samtidig som du slipper at sand, strø og høy søles ut i rommet. Ikke la degusene gå direkte på gitterbunn eller annet hardt underlag, det kan skade føttene.

Buret kan du innrede med f.eks. røtter og greiner til å klatre på, hus av treverk, rør til å krype gjennom og løpehjul. Et løpehjul til degus bør være minst 25 cm i diameter og ha tett gulv og vegger slik at halen ikke kan komme i klem. Bunnmaterialet i buret bør være et tykt lag av støvfritt smådyrstrø som er egnet for graving. Det finnes flere egnede strøtyper å få kjøpt. Bland gjerne inn litt tørr blomsterjord eller sand i bunnmaterialet. Hvis du henter sand ute, bør du desinfisere den ved frysing eller steking fr den brukes i buret. Degusene trenger også tilgang på fiberrikt materiale som høy, revet papir eller treull til bygge- og redemateriale.

For å være sikker på at alle degusene som bor sammen kan trekke seg unna og hvile, bør de få hvert sitt sovehus. Deguser kan også finne på å forsvare maten sin overfor andre deguser. Når flere deguser bor i samme bur, bør du derfor ha flere matskåler plassert på forskjellige steder i buret slik at alle får tilgang til mat når de ønsker det. Dyrene må alltid ha tilgang på friskt vann, som best gis i en drikkeflaske.

For å holde pelsen i orden har deguser behov for å bade i finkornet sand flere ganger i uka. Slik badesand får du kjøpt i dyrebutikken. Et tungt kar som ikke velter så lett er fint som sandbadekar. Det kan være lurt å fjerne sandbadet mellom hvert bad for å unngå at den brukes som toalett.

Rengjøring

Hvor ofte buret bør rengjøres avhenger av størrelsen og hvor mange som bor der. Som en tommelfingerregel bør du skifte bunnmaterialet og vaske bunn og innredning én gang i uka.

\section{Experiments}

\section{Results}

\section{Conclusion}

@@

I would like to acknowledge myself for being a absolute legend.

@@
